### 2018-11-23 Sections/optical_routers.tex
Formatting, algs
Posted Rohit's first contrib.

We will use the terminology that:
\begin{itemize}
	\item \textit{Ports}\index{Ports}: refers to the number of input and output optical modes in a device.
	\item \textit{Channels}\index{Channels}: refers to the number of simultaneous communications streams running in parallel through the device.
	\item \textit{Optical depth}\index{Optical!Depth}: is the number of primitive optical elements/devices an optical path traverses through the course of its trajectory from input to output.
\end{itemize}

A summary of the routing devices we consider, and their associated resource requirements, is provided in Table.~\ref{tab:router_summary}.

@@

\subsection{Interferometric routers} \index{Interferometric routers}

@@

%
% Phase-Modulators
%

\subsubsection{Phase-modulators} \index{Phase-modulators}

A phase-modulator is a classically-controlled device that lets us tune the local phase accumulated by an optical path, ideally over the full range of $\{0,2\pi\}$. These may be implemented in several ways:

\comment{Rohit helps here}

@@

\paragraph{Electro-optic modulators} \index{Electro-optic modulators}

\comment{here an applied electric field induces a change in refractive index in a medium, causing a phase-shift.}

\comment{To do! Explain how these work}

@@

\paragraph{Acousto-optic modulators} \index{Acousto-optic modulators}

\comment{an applied acoustic wave generated by a piezoelectric transducer induces a change in refractive index in a medium, causing a phase-shift}

\comment{To do! Explain how these work}

@@

\paragraph{Magneto-optic modulators} \index{Magneto-optic modulators}

\comment{an applied magnetic field induces the change in refractive index}

\comment{To do! Explain how these work}

%
% Pockels Cells
%

\paragraph{Pockels cells} \index{Pockels cells}

\comment{act as voltage-controlled wave-plates, 	which take the place of phase-shifters in a polarisation-encoded version of Mach-Zehnder interference.}

\comment{To do! Explain how these work}

@@

\subsubsection{Two-channel two-port switches} \index{Two-channel two-port switches}

@@

\subsubsection{Multiplexers \& demultiplexers} \index{Multiplexers}\index{Demultiplexers}

@@

\subsubsection{Single-channel multi-port switches} \index{Single-channel multi-port switches}

@@

\subsubsection{Multi-channel multi-port switches} \index{Multi-channel multi-port switches}

@@

\subsubsection{Crossbar switches}\index{Crossbar switches}

>>>>

We will use the terminology that:
\begin{itemize}
	\item \textit{Ports}\index{Ports}: refers to the number of input and output optical modes in a device.
	\item \textit{Channels}\index{Channels}: refers to the number of simultaneous communications streams running in parallel through the device.
	\item \textit{Optical depth}\index{Optical!Depth}: is the number of primitive optical elements/devices an optical path traverses through the course of its trajectory from input to output.
	\item \textit{Directionality}\index{Directionality}: whether information is transferred in one or two directions.
	\item \textit{Switching time}\index{Switching time}: Time for the switch to get configured from one state to another state.
	\item \textit{Delay time}\index{Delay time}: time taken by signal to reach the output line of the switch from input.
	\item \textit{Throughput}\index{Throughput}: maximum data rate that can flow through the switch.
	\item \textit{Switching energy}\index{Switching energy}: energy needed for activating and deactivating the switch.
	\item \textit{Power dissipation}\index{Power dissipation}: energy dissipated per second in the process of switching.
	\item \textit{Insertion loss}\index{Insertion loss}: loss in signal power when the switch is connected.
	\item \textit{Crosstalk}\index{Crosstalk}: the power leaked to other lines.
\end{itemize}

A summary of the routing devices we consider, and their associated resource requirements, is provided in Tab.~\ref{tab:router_summary}.

@@

\subsection{Interferometric switches} \index{Interferometric switches}

@@

A phase modulator\index{Phase modulators} is a classically-controlled device that lets us tune the local phase accumulated by an optical path, ideally over the full range of $\{0,2\pi\}$. These may be implemented in several ways:

@@

\subsubsection{Electro-optic modulators} \index{Electro-optic modulators}

There are materials called anisotropic materials\index{Anisotropic materials}, in which the refractive indices change due to an applied electric field. Based upon the change these effects are classified into two -- Pockel's effect\index{Pockel's effect} and Kerr effect\index{Kerr effect}.

The effect is called Pockel's effect or linear electro optic effect when the refractive index\index{Refractive index} change is in proportion to the applied electric field.

The effect is named Kerr effect or quadratic electro optic effect when the refractive index change is in proportion to the square of the applied electric field. These changes in refractive indices are typically smaller such that, the effects are significant on optical waves when they propagate distances larger than wavelength of light. For example, in a material the refractive index increases by $10^{-4}$, then an optical wave propagating a distance of $10^{-4}$ wavelengths will experience and an additional phase-shift of $2\pi$.

The refractive index of an electro-optic medium is a function $n(E)$ of the applied electric field $E$. This function varies only slightly with $E$, such that using Taylor series expansion\index{Taylor series} about \mbox{$E=0$},
\begin{align}
n(E) = n+a_1E + \frac{1}{2}a_2E^2+\dots.
\end{align}

In a Pockel's medium\index{Pockel's medium} this relation becomes (after approximating and simplifying),
\begin{align}
n(E) = n-\frac{1}{2}\chi n^3 E,
\end{align}
where $\chi$ is called the Pockel's coefficient\index{Pockel's coefficient} or the linear electro-optic coefficient. Typical values of $\chi$ lies in the range $10^{-12}-10^{-10}$mV$^{-1}$. The common crystals used as Pockel's cells are NH$_4$H$_2$PO$_4$ (ADP), KH$_2$PO$_4$ (KDP), LiNbO$_3$, LiTaO$_3$, and CdTe.

In a centrosymmetric material\index{Centrosymmetric material} or Kerrs's medium\index{Kerr's medium} this relation turns out as (again after approximating and simplifying),
\begin{align}
n(E) = n-\frac{1}{2}\xi n^3 E^2,
\end{align}
where $\xi$ is the Kerr's coefficient\index{Kerr's coefficient} or the quadratic electro-optic coefficient whose typical values of $\xi$ lies in the range $10^{-18}-10^{-14}$m$^2$V$^{-2}$.

\begin{figure}[!htbp]
\caption{Dependence of refractive index on electric field in: (a) Pockel's medium (b) Kerr's medium. ???}
\end{figure}

Light signal when transmitted through a transparent plate of controllable refractive index undergoes controllable phase shift. This plate can be used as an optical phase modulator.

Consider a light signal traversing a Pockets cell of length $L$ to which an electric field $E$ is applied. The phase-shift undergone is given by,

\begin{align}
\phi \approx \phi_0 - \pi\frac{\chi n^3 E L}{\lambda_0},
\end{align}
where,
\begin{align}
\phi_0 = \frac{2\pi nL}{\lambda_0}.
\end{align}

If electric field generated by applying a voltage $V$ across the faces of the cell of dimension $d$, is,
\begin{align}
	E=\frac{V}{d},
\end{align}
then,
\begin{align}
	\phi=\phi_0-\pi \frac{V}{V_\pi},
\end{align}
where,
\begin{align}
	V_\pi=\frac{d\lambda_0}{L\chi n^3},
\end{align}
half-wave voltage, is the applied voltage at which the phase shift changes by $\pi$.

The electric field is applied either perpendicular (transverse modulators\index{Transverse modulators}) or parallel (longitudinal modulators\index{Longitudinal modulators}) to the direction of light signal propagation. The value of the electro-optic coefficient $\chi$ depends on the directions of propagation and the applied field. The speed of operation is limited by the capacitive effects and the transit time of the signal through the material.

State of the art electro-optic modulators are integrated optic devices based on LiNbO$_3$ in which materials like titanium are used to increase the refractive index. The typical operation speed is above 100GHz. Light signals can be coupled in and out using optical fibres.

@@

\subsubsection{Acousto-optic modulators} \index{Acousto-optic modulators}

Sound or acoustic waves are vibrations that travel through a medium with a velocity that is characteristic of the medium. This can create perturbations the refractive index of the optical medium, thus modifying the velocity of the light signal passing through the medium. Thus sound can be used to modify the effect of the medium on light, in other words, sound can control light. This acousto-optic effect is used to make a variety of devices like optical modulators, switches, deflectors, filters, isolators, frequency shifters and spectrum analysers.

The refractive index of an optical medium is altered by the presence of sound. Sound therefore modifies the effect of the medium on light; i.e., sound can control light (Fig. ????). Many useful devices make use of this acousto-optic effect; these include optical modulators, switches, deflectors, filters, isolators, frequency shifters, and spectrum analysers.

\begin{figure}[!htbp]
\caption{Acousto-optic modulators.}
\end{figure}

According to the quantum theory, light wave of angular frequency $\omega$ and wave-vector $k$ is a stream of photons each with energy $\hbar\omega q$ and angular momentum $\hbar k$. Also, sound wave of acoustic frequency $\Omega$ and wave vector $q$, is a stream of phonons each with energy $\hbar\Omega$ and momentum $\hbar q$. When light and sound interacts, photon combines with a phonon to generate a new photon with energy, 
\begin{align}
\hbar\omega_r = \hbar\omega + \hbar\Omega,
\end{align}
and wave-vector,
\begin{align}
\hbar k_r = \hbar k + \hbar q.
\end{align}

\begin{figure}[!htbp]
\caption{???}
\end{figure}

Since the intensity of the reflected light is proportional to the intensity of the sound (provided the intensity of sound is low), the intensity of reflected light can be varied proportionally by using an electrically controlled acoustic transducer. This device can be used as a linear modulator of light.

When the acoustic power increases beyond a certain level, total reflection of light occurs and at this stage the modulator becomes an optical switch. By switching the sound on and off, the reflected light can be turned on and off, which makes the transmitted light off and on, as illustrated in the figure????.

\begin{figure}[!htbp]
\caption{???}
\end{figure}

@@

\subsubsection{Magneto-optic modulators} \index{Magneto-optic modulators}

In the presence of a static magnetic field, certain materials act as polarisation rotators, which is known as Faraday effect. The angle of rotation is proportional to the distance and the rotary power $\rho$ (angle per unit length), is proportional to the component $B$ of the magnetic flux density in the direction of wave propagation,
\begin{align}
	\rho=VB,
\end{align}
where $V$ is known as the Verdet constant, which is a function of wavelength $\lambda_0$.

Examples of materials that exhibit Faraday effect include glass, Yttrium-iron-garnet (YIG), Terbium-gallium-garnet (TGG) and Terbium-aluminium-garnet (TbAlG). The Verdet constant, of TbAlG is $V=-1.16$min/cm-Oe \comment{What are these units?} at $\lambda_0=500$nmV.

\begin{figure}[!htbp]
\caption{???}
\end{figure}

A simple form of magneto-optic modulator consists of a parallel-sided disk of material placed in a small coil. An alternating current in the coil gives a magnetic field normal to the plane of the disk. The material becomes magnetised in this direction and light propagating through the disk suffers a rotation of its plane of polarisation. The modulation of the angle of the plane of polarisation induced by the alternating current is converted to amplitude modulation by passing the beam through a polariser.

@@

\subsection{Two-channel two-port switches} \index{Two-channel two-port switches}

@@

\subsection{Multiplexers \& demultiplexers} \index{Multiplexers}\index{Demultiplexers}

@@

\subsection{Single-channel multi-port switches} \index{Single-channel multi-port switches}

@@

\subsection{Multi-channel multi-port switches} \index{Multi-channel multi-port switches}

@@

\subsection{Crossbar switches}\index{Crossbar switches}
